---
title: "Yogurt Flavor Code"
date: "2/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


############################## SQL CODE - Q1 ##############
select sum(Units) 'Units Sold',Class, Flavor1, Brand, sum(Sales) sales,sum(Sales)/sum(Units) price
from storeItemSales join itemsAttributes on storeItemSales.`Item.Num`  = itemsAttributes.`Item.Num`
where Class='Greek'
group by Class, Brand, Flavor1;
#############################          ###############

############################   SQL CODE - Q2 #################
select sum(Units) 'Units Sold',Class, Flavor1, Brand, sum(Sales) sales,sum(Sales)/sum(Units) price
from storeItemSales join itemsAttributes on storeItemSales.`Item.Num`  = itemsAttributes.`Item.Num`
where  Class ='Regular'
group by Class,Brand, Flavor1;
###########################               ##################


```{r}
rm(list=ls())
library(foreign)
library(ggplot2)
setwd("/Users/zhaoyiqun/Desktop/")
sur = read.csv("survResponse.csv")

```

##Data Cleaning
```{r}
# 1) delete those surveys that took an unusually long time to complete
t.test(as.numeric(difftime(surv$V9, surv$V8, units = "mins"))) # 95% between 10.5 & 45 min
surv <- surv[difftime(surv$V9, surv$V8, units = "mins") <= 45,]
# 2) delete those incomplete surveys
surv <- surv[,-c(2:14)]
surv <- surv[rowSums(is.na(surv)) < ncol(surv)-1, ] # delete the rows that only contain NA
surv[,2:24][is.na(surv[,2:24])] <- 3 # replace all the NA in col 2-24 with another number 3
names(surv)[2:24] <- c('Almond','Banana','Black Cherry','Buleberry','Caramel',
                       'Chai','Chocolate','Cinnamon','Coconut','Honey',
                       'Key Lime Pie','Lemon','Mango','Maple','Peach','Pineapple',
                       'Plain','Pomegranate','Raspberry','Strawberry',
                       'Strawberry Banana','Vanilla','Vanilla Banana')
```

## Output for Slide 4 (Q3) 
```{r}
freq <- data.frame(Regularly = colSums(surv[2:24]==0),
                   Occasionally = colSums(surv[2:24]==1),
                   Never = colSums(surv[2:24]==2))
# colSums(Boolean data type): return the number of TRUE value each col
freq$RegFreq <- freq$Regularly/rowSums(freq)
freq$OccFreq <- freq$Occasionally/rowSums(freq)
freq$NevFreq <- freq$Never/rowSums(freq)
freq[freq$RegFreq == max(freq$RegFreq),] # Bluberry is the most popular flavor
```


## Output for Slide 5 (Q4)
```{r}
for (i in 1:696){
  for (j in 2:24){
    if (surv[i,j]==0){
      surv[i,j] = 10
    } else if (surv[i,j]==1 | surv[i,j]==2 | surv[i,j]==3){
      surv[i,j] = 0
    }
    if(surv[i,j]==10){
      surv[i,j] = 1
    }
  }
}

# measReach: measures reach given set of options and data
# Arguments:
# data contains measure of proxy for whether will buy or not, positive values mean will buy/use
# Return:
# scalar, reach, calculated as % of all cases that will buy at least one in set
measReach = function(data){
  if(is.null(dim(data))){ #if data is a vector
    ret = sum(data>0,na.rm=TRUE)/length(data)
  } else if(ncol(data)==1){ #if data has only one column
    ret = sum(data>0,na.rm=TRUE)/length(data)
  }
  else { #if data has multiple columns
    ret = sum(apply(data>0,1,any),na.rm=TRUE)/nrow(data)
  }                        # any: check is any of the value is true
}
# evalNext: evaluates the next set, nextSet using measure given existing set in data
# Arguments:
#   nextSet, set are numeric indexes into columns of data
#   data contains measure of proxy for whether will buy or not, positive values mean will buy/use
#   measure is a valid measure of evaluation when passed a subset of columns in data
# Return:
#   numeric vector of values calculated using measure for each option in nextSet given set already exists
evalNext = function(nextSet,set,data,measure=measReach){
  vals = numeric(length(nextSet)) #set up storage for return value
  for(k in 1:length(nextSet)){ #loop over the options in nextSet
    if(length(set)==0){         #if no existing options
      vals[k] = measure(data[,nextSet[k]]) 
    } else {                    #if existing options
      vals[k] = measure(data[,c(set,nextSet[k])])
    }
  }
  vals
}
# evalFull: creates optimal full evaluation starting from origSet and considering remaining options fullSet
# Arguments:
#   fullSet, origSet are numeric indexes into columns of data
#   data contains measure of proxy for whether will buy or not, positive values mean will buy/use
#   measure is a valid measure of evaluation when passed a subset of columns in data
# Return:
#   turf object, an named list containing
#   ordSet, the ordered set of optimal options to add to original set
#   optVals, the optimal values of measure as you add each optimal option
#   origSet, same value as passed, the original set of options included
#   origVal, the value of measure for the original set
#   measure, same value as passed, the measure used
#   pnames, the names of the options taken from the columns of data
evalFull = function(fullSet,data,origSet=numeric(0),measure=measReach){
  curSet = origSet; #the current set of included options
  remSet = fullSet[!(fullSet%in%origSet)]; #the remaining set of options to consider
  K = length(remSet)
  optVals = numeric(K); #create storage for the optimal values (optVals)
  ordSet = numeric(K); #create storage for ordered set
  for(i in 1:K){          #loop over the remaining set consider
    tmpVals = evalNext(remSet,curSet,data,measure); #calculate vector of next evaluations
    k = which.max(tmpVals) #pick the option that gives max measure, note will pick first case if a tie!
    optVals[i] = tmpVals[k] #add optimal value
    ordSet[i] = remSet[k]   #add index of option that creates optimal value
    curSet = c(curSet,ordSet[i]); #add optimal next option to current set
    remSet = remSet[-k];          #delete optimal next option from remaining set
  }
  #creaets a "TURF object" containing ordSet, optVals, origSet, origVal, measure, and pnames
  turf = list(ordSet=ordSet,optVals=optVals,origSet=origSet,origVal=measure(data[,origSet]),measure=measure,pnames=colnames(data))
  class(turf)="TURF" #makes the list into a TURF object so that can call plot.TURF
  turf  #return turf
}
# creates ggplot barplot for a turf object
plot.TURF=function(turf,...){
  if(class(turf)!="TURF"){
    cat("Object not a turf.")
  } else {
    df = with(turf,data.frame(vals = c(origVal,optVals),titles=paste(0:length(ordSet),c("Original",pnames[ordSet]),sep=":")))
    #with(turf,barplot(c(origVal,optVals),names.arg=c("Original",pnames[ordSet])))
    dodge = position_dodge(width=.75); ##to form constant dimensions positioning for all geom's
    gp = ggplot(df,aes(y=vals,x=titles))
    gp + geom_bar(position=dodge,stat="identity",col=1,fill=4,width=.75)
  }
}

brandsPurch = surv[,2:24]
#names(brandsPurch)=substr(names(brandsPurch),10,100)
turf = evalFull(c(1:23),brandsPurch,c(4,10,15,17,20,22))
plot(turf)
```
